Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
:q
double paths

%\begin{figure}[t]
%	\capstart
%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded. The first surface is a cylinder, the second one is a torus with a hole.}
%	\label{fig:examplesSurfaces2}
%\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{example}[Double paths]
\label{exm:doublePath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}

@@

\begin{lemma}
\label{lemm:facesAreBounded}
There is a bound on the number of elements of a finite face of~$\NKC$.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.

@@

\begin{lemma}
\label{lemm:facetsAreFinite}
Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
\end{lemma}
\begin{proof}
 This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
\end{proof}

>>>>

Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{example}[Double paths]
\label{exm:doublePath}
Consider the family ``double paths'' quivers indicated in \fref{fig:doublePathsQuivers}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.4]{doublePathsQuivers}}
	\caption{The double paths quivers with~$1, 2, 3, 4$ vertices.}
	\label{fig:doublePathsQuivers}
\end{figure}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{doublePathsSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the double paths with~$1, 2, 3, 4$ vertices.}
	\label{fig:doublePathsSurfaces}
\end{figure}

\end{example}

@@

\begin{lemma}
\label{lemm:facesAreBounded}
There is a bound on the number of elements of a finite face of~$\NKC$.
\end{lemma}

\begin{lemma}
\label{lemm:facetsAreFinite}
Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.

 {\it Combinatorial proof.}
 This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.

@@
